Appendix 3: Estimating species interactions

### 2015-10-25 Harris_2015/recovery.Rmd
various

```{r, cache = TRUE, message = FALSE}
library(dplyr)        # For manipulating data structures
library(corpcor)      # For regularized partial covariances
library(rosalia)      # For Markov networks
library(arm)          # For regularized logistic regression
library(BayesComm)    # For joint species distribution modeling
library(RColorBrewer) # For color palette
set.seed(1)
```

@@

```{r, cache = TRUE}
pairs_txt = readLines("fakedata/Pairs.txt")

# Find areas of the data file that correspond
# to species pairs' results
beginnings = grep("Sp1", pairs_txt) + 1
ends = c(
  grep("^[^ ]", pairs_txt)[-1],
  length(pairs_txt)
) - 1

# The above code fails on the very last line of the file
ends[length(ends)] = ends[length(ends)] + 1
```

@@

```{r, cache = TRUE}
fit_all = function(filename){
  ######## Import ########

  # Multiplying by one is necessary to prevent silly errors
  # regarding TRUE/FALSE versus 1/0
  raw_obs = readRDS(filename)[["observed"]] * 1

@@

  x = raw_obs[ , species_is_variable]
  truth = readRDS(filename)[["truth"]][pair_is_variable[upper.tri(pair_is_variable)]]

  splitname = strsplit(filename, "/|-|\\.")[[1]]
  n_sites = as.integer(splitname[[3]])
  rep = as.integer(splitname[[4]])

@@

  ######## Correlations ########
  corr = cor(x)

  ######## GLM ########
  coef_matrix = matrix(0, ncol(x), ncol(x))
  for(i in 1:ncol(x)){
    if(var(x[,i]) > 0){
      coefs = coef(bayesglm(x[,i] ~ x[ , -i], family = binomial))[-1]
      coef_matrix[i, -i] = coefs
    }
  }
  coef_matrix = (coef_matrix + t(coef_matrix)) / 2

  ######## Markov network ########
  rosie = rosalia(x, maxit = 200, trace = 0, prior = make_logistic_prior(scale = 2))

@@

  `partial BayesComm` = 0

  for(i in 1:nrow(bc$trace$R)){
    Sigma = matrix(0, nrow = ncol(x), ncol = ncol(x))
    Sigma[upper.tri(Sigma)] <- bc$trace$R[i, ]  # Fill in upper triangle
    Sigma <- Sigma + t(Sigma)                   # Fill in lower triangle
    diag(Sigma) <- 1  # Diagonal equals 1 in multivariate probit model

    `partial BayesComm` = `partial BayesComm` + cor2pcor(Sigma) / nrow(bc$trace$R)
  }

  ######## Pairs ########
  # Find the line where the current data set is mentioned in
  # pairs.txt
  filename_line = grep(
    paste0(
      gsub("fakedata/(.*)\\.rds", "\\1", filename),
      "-"
    ),
    pairs_txt
  )

  # Which chunk of the data file corresponds to this file?
  chunk = min(which(beginnings > filename_line))

  # Split the chunk on whitespace.
  splitted = strsplit(pairs_txt[beginnings[chunk]:ends[chunk]], " +")

  # Pull out the species numbers and their Z-scores
  pairs_results = lapply(
    splitted,
    function(x){
      spp = sort(as.integer(x[3:4]))
      data.frame(
        sp1 = spp[1], 
        sp2 = spp[2], 
        z = as.numeric(x[14])
      )
    }
  ) %>% 
    bind_rows %>%
    mutate(spp = paste(sp1, sp2, sep = "-"))

  # Re-order the pairs_results to match the other methods
  m = matrix(NA, ncol(x), ncol(x))
  new_order = match(
    paste(row(m)[upper.tri(m)], col(m)[upper.tri(m)], sep = "-"),
    pairs_results$spp
  )
  ordered_pairs_results = pairs_results[new_order, ]

  ######## Output ########
  data.frame(
    truth = truth, 
    n_sites = n_sites,
    rep = rep,
    sp1 = ordered_pairs_results$sp1,
    sp2 = ordered_pairs_results$sp2,
    `partial correlation` = p_corr[upper.tri(p_corr)],
    correlation = corr[upper.tri(corr)],
    `Markov network` = rosie$beta[upper.tri(rosie$beta)],
    GLM = coef_matrix[upper.tri(coef_matrix)],
    `BayesComm` = colMeans(bc$trace$R),
    `partial BayesComm` = `partial BayesComm`[upper.tri(`partial BayesComm`)],
    Pairs = ordered_pairs_results$z
  )
}
```

@@

```{r, cache = TRUE}

# Find all the .rds files in the fakedata folder
files = dir("fakedata", pattern = "\\.rds$", full.names = TRUE)

# Run all the analyses on all the files
z = lapply(files, fit_all) %>% bind_rows %>% as.data.frame

# Fix a formatting issue with the column names
colnames(z) = gsub("\\.", " ", colnames(z))
```

Summarize the results of all 7 methods across the simulated landscapes:

```{r, cache = TRUE}

# Calculate residuals for each method
resids = sapply(
  colnames(z)[-(1:5)],
  function(i){resid(lm(z$truth ~ z[,i] + 0))}
)

sizes = sort(unique(z$n_sites))

# Compute proportion of variance explained, compared with a null that
# assumes all species interactions are 0.
results = as.data.frame(
  t(
    sapply(
      sizes,
      function(n){
        total_ss = mean(resid(lm(truth ~ 0, data = z))[z$n_sites == n]^2)
        1 - colMeans(resids[z$n_sites == n , ]^2) / total_ss
      }
    )
  )
)
# Sort the results in decreasing order
results = results[order(colMeans(results), decreasing = TRUE)]
```

Plot the results:

```{r, cache = TRUE, message=FALSE}
colors = brewer.pal(8, "Dark2")[c(1, 2, 3, 4, 8, 5, 7)]

# Set up the plotting canvas
pdf("manuscript-materials/figures/performance.pdf", height = 8, width = 5)
par(mfrow = c(2, 1))
par(mar = c(5, 4, 3, 0) + .1)

# Plot the model performance
matplot(
  sizes, 
  results, 
  type = "o", 
  ylab = "", 
  xlim = c(25 * .9, 1600 * 8),
  ylim = c(0, .5 + 1E-9),
  pch = c(15, 1, 17, 0, 16, 2, 3), 
  lty = 1,
  log = "x",
  xlab = "",
  axes = FALSE,
  xaxs = "i",
  yaxs = "i",
  col = colors,
  lwd = 1.25,
  cex = 0.9,
  bty = "l"
)
axis(1, c(1, 25, 200, 1600))
axis(2, seq(0, 1, .1), las = 1)

mtext(expression(R^2), side = 2, line = 3, las = 1)
mtext("Number of sites (log scale)", side = 1, line = 2.25, at = 200)
mtext("A.", line = 1.25, at = 25, cex = 1.5)

# Determine how high on the y-axis each method label should be so they
# don't overlap.
heights = results[nrow(results), ]

heights$Pairs = heights$Pairs - .01
heights$correlation = heights$correlation + .01

heights$`partial correlation` = heights$`partial correlation` + .01
heights$`partial BayesComm` = heights$`partial BayesComm` - .01

heights$GLM = heights$GLM - .01

text(1625, heights, colnames(results), pos = 4, cex = 0.75, col = colors)

######

# silly code to make the next graph line up prettily with the previous one
full_range = log10(c(25 * .9, 1600 * 8))
base_range = log10(c(25, 1600))

base_scaled = 2 * base_range / (base_range[2] - base_range[1])
full_scaled = 2 * full_range / (base_range[2] - base_range[1])

# New colors for plot B
colors2 = brewer.pal(10, "Paired")[c(2, 4, 10)]
plot(
  z$correlation, 
  z$Pairs, 
  col = colors2[factor(z$n_sites)],
  las = 1,
  xlab = "",
  ylab = expression(italic(Z)-score),
  bty = "l",
  xaxs = "i",
  axes = FALSE,
  xlim = full_scaled - base_scaled[2] + 1
)
axis(1, seq(-2, 1, .5))
axis(2, seq(-50, 50, 10), las = 1)
mtext("Correlation coefficient", side = 1, line = 2.25, at = 0)
mtext("B.", line = 1.25, at = -1, cex = 1.5)

legend(
  x = 1.05, 
  y = max(z$Pairs),
  pch = 1,
  lty = 0,
  lwd = 2,
  col = colors2[1:length(unique(z$n_sites))], 
  legend = levels(factor(z$n_sites)),
  title = "Number of sites",
  bty = "n",
  cex = 0.75,
  pt.cex = 1
)
segments(-1000, 0, 1.04, 0, col = "#00000025", lwd = 1.25)
segments(0, -1000, 0, 1000, col = "#00000025", lwd = 1.25)

dev.off()
```

![Figure 3](manuscript-materials/figures/performance.pdf)

Summarize the results:

```{r, cache = TRUE}

# R-squareds computed across *all* landscape types
total_ss = mean(resid(lm(truth ~ 0, data = z))^2)
round(100 * sort(1 - colMeans(resids^2) / total_ss), 1)

# Rank correlations among the methods that estimate marginal relationships
round(cor(z[ , c(7, 10, 12)], method = "spearman")[,1], 2)
```

Plot the true interactions versus estimated interactions for two methods:

```{r, cache = TRUE}
library(ggplot2)

ggplot(z[z$n_sites >0, ], aes(x = `Markov network`, y = truth)) + 
  stat_binhex(bins = 100) + 
  xlab("Estimated coefficient value") + 
  ylab("\"True\" coefficient value") + 
  stat_hline(yintercept = 0, size = 1/8) + 
  stat_vline(xintercept = 0, size = 1/8) + 
  scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
  theme_bw() + 
  ggtitle("Markov network") + 
  stat_abline(intercept = 0, slope = coef(lm(z$truth ~ z$`Markov network` + 0)))

ggplot(z[z$n_sites >0, ], aes(x = `Pairs`, y = truth)) + 
  stat_binhex(bins = 100) + 
  xlab("Estimated coefficient value") + 
  ylab("\"True\" coefficient value") + 
  stat_hline(yintercept = 0, size = 1/8) + 
  stat_vline(xintercept = 0, size = 1/8) + 
  scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
  theme_bw() + 
  ggtitle("Null model (\"Pairs\")") + 
  stat_abline(intercept = 0, slope = coef(lm(z$truth ~ z$Pairs + 0)))
```

Bootstrap resample from each of the three landscape size classes, generating
new sets of 150 landscapes. For each one, calculate the proportion of variance
explained (compared to a null baseline that assumes all species pairs' 
interaction strengths are zero).

```{r, cache = TRUE}
rep = 12
n = 200
boots = replicate(500,
          {
            boot = lapply(
              sizes, 
              function(n){lapply(
                sample.int(max(z$rep), replace = TRUE),
                function(rep){
                  z[z$rep == rep & z$n_sites == n, ]
                }
              ) %>% bind_rows}
            ) %>% bind_rows

            resids = sapply(
              colnames(boot)[-(1:5)],
              function(i){resid(lm(boot$truth ~ boot[[i]] + 0))}
            )
            total_ss = mean(resid(lm(truth ~ 0, data = boot))^2)
            1 - colMeans(resids^2) / total_ss
          }
)
```

Summarize the bootstrap results:

```{r, cache = TRUE}
for(compared in c("partial correlation", "correlation", "GLM", "BayesComm", "partial BayesComm", "Pairs")){
  CI = round(
    quantile(
      boots["Markov network", ] / boots[compared, ], 
      c(.025, .975)), 
    2
  )

  message("R-squared is " , CI[1], "-", CI[2], " times higher than from ", compared, " (95% bootstrap CI)")
}
```

>>>>

```{r, cache = FALSE, message = FALSE, eval = TRUE}

mc.cores = 2

library(dplyr)        # For manipulating data structures
library(corpcor)      # For regularized partial covariances
library(rosalia)      # For Markov networks
library(arm)          # For regularized logistic regression
library(BayesComm)    # For joint species distribution modeling
library(parallel)     # for mclapply
set.seed(1)
```

@@

@@

```{r, cache = FALSE, eval = TRUE}
fit_all = function(identifier){
  ######## Import ########

  data_filename = paste0("fakedata/matrices/", identifier, ".csv")
  truth_filename = paste0("fakedata/truths/", identifier, ".txt")

  # first column is row numbers; drop it
  raw_obs = as.matrix(read.csv(data_filename)[ , -1])

@@

  x = raw_obs[ , species_is_variable]
  truth = unlist(read.table(truth_filename))[pair_is_variable[upper.tri(pair_is_variable)]]

  splitname = strsplit(identifier, "/|-|\\.")[[1]]
  n_spp = as.integer(splitname[[1]]) # simulated species, NOT present species
  n_sites = as.integer(splitname[[2]])
  rep_name = splitname[[3]]

  # Species IDs
  sp1 = combn(colnames(x), 2)[1, ]
  sp2 = combn(colnames(x), 2)[2, ]

@@

  ######## Correlations ########
  corr = cor(x)
  ######## GLM ########
  coef_matrix = matrix(0, ncol(x), ncol(x))
  for(i in 1:ncol(x)){
    if(var(x[,i]) > 0){
      coefs = coef(bayesglm(x[,i] ~ x[ , -i], family = binomial))[-1]
      coef_matrix[i, -i] = coefs
    }
  }
  coef_matrix = (coef_matrix + t(coef_matrix)) / 2

  ######## Markov network ########
  rosie = rosalia(x, maxit = 200, trace = 0, prior = make_logistic_prior(scale = 2), hessian = TRUE)

  rosie_point = rosie$beta[upper.tri(rosie$beta)]
  rosie_se = sqrt(diag(solve(rosie$opt$hessian)))[-(1:sum(species_is_variable))]

@@

  bc_pcors = sapply(
    1:nrow(bc$trace$R), 
    function(i){
      Sigma = matrix(0, nrow = ncol(x), ncol = ncol(x))
      Sigma[upper.tri(Sigma)] <- bc$trace$R[i, ]  # Fill in upper triangle
      Sigma <- Sigma + t(Sigma)                   # Fill in lower triangle
      diag(Sigma) <- 1  # Diagonal equals 1 in multivariate probit model
      pcor = cor2pcor(Sigma)
      pcor[upper.tri(pcor)]
    }
  )

  bind_rows(
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "Markov network",
      truth = truth,
      estimate = rosie_point, 
      lower = qnorm(.025, rosie_point, rosie_se), 
      upper = qnorm(.975, rosie_point, rosie_se)
    ),
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "GLM",
      truth = truth,
      estimate = coef_matrix[upper.tri(coef_matrix)], 
      lower = NA, 
      upper = NA
    ),
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "correlation",
      truth = truth,
      estimate = corr[upper.tri(corr)], 
      lower = NA, 
      upper = NA
    ),
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "partial correlation",
      truth = truth,
      estimate = p_corr[upper.tri(p_corr)], 
      lower = NA, 
      upper = NA
    ),
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "partial BayesComm",
      truth = truth,
      estimate = rowMeans(bc_pcors),
      lower = apply(bc_pcors, 1, quantile, .025),
      upper = apply(bc_pcors, 1, quantile, .975)
    ),
    data_frame(
      rep_name = rep_name,
      n_sites = n_sites,
      sp1 = sp1,
      sp2 = sp2,
      method = "BayesComm",
      truth = truth,
      estimate = colMeans(bc$trace$R),
      lower = apply(bc$trace$R, 2, quantile, .025),
      upper = apply(bc$trace$R, 2, quantile, .975)
    )
  )
}
```

@@

```{r, cache = FALSE, eval = TRUE}

# Find all the csv files in the fakedata/matrices folder,
# then drop .csv
identifiers = dir("fakedata/matrices", pattern = "\\.csv$") %>%
  gsub("\\.csv$", "", .)

mclapply(identifiers, fit_all, mc.cores = mc.cores, mc.preschedule = FALSE, mc.silent = TRUE) %>% 
  bind_rows() %>% 
  write.csv(file = "estimates.csv")
```

### 2015-10-25 Harris_2015/recovery.tex
various

\CommentTok{# Run all the analyses on all the files}
\NormalTok{z =}\StringTok{ }\KeywordTok{lapply}\NormalTok{(files, fit_all) %>%}\StringTok{ }\NormalTok{bind_rows %>%}\StringTok{ }\NormalTok{as.data.frame}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Fix a formatting issue with the column names}
\KeywordTok{colnames}\NormalTok{(z) =}\StringTok{ }\KeywordTok{gsub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{."}\NormalTok{, }\StringTok{" "}\NormalTok{, }\KeywordTok{colnames}\NormalTok{(z))}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# R-squareds computed across *all* landscape types}
\NormalTok{total_ss =}\StringTok{ }\KeywordTok{mean}\NormalTok{(}\KeywordTok{resid}\NormalTok{(}\KeywordTok{lm}\NormalTok{(truth ~}\StringTok{ }\DecValTok{0}\NormalTok{, }\DataTypeTok{data =} \NormalTok{z))^}\DecValTok{2}\NormalTok{)}
\KeywordTok{round}\NormalTok{(}\DecValTok{100} \NormalTok{*}\StringTok{ }\KeywordTok{sort}\NormalTok{(}\DecValTok{1} \NormalTok{-}\StringTok{ }\KeywordTok{colMeans}\NormalTok{(resids^}\DecValTok{2}\NormalTok{) /}\StringTok{ }\NormalTok{total_ss), }\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##           BayesComm               Pairs         correlation 
##                11.6                15.4                18.6 
##   partial BayesComm partial correlation                 GLM 
##                26.1                27.5                29.9 
##      Markov network 
##                34.6
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Rank correlations among the methods that estimate marginal relationships}
\KeywordTok{round}\NormalTok{(}\KeywordTok{cor}\NormalTok{(z[ , }\KeywordTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{12}\NormalTok{)], }\DataTypeTok{method =} \StringTok{"spearman"}\NormalTok{)[,}\DecValTok{1}\NormalTok{], }\DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## correlation   BayesComm       Pairs 
##        1.00        0.85       -0.92
\end{verbatim}

@@

\KeywordTok{ggplot}\NormalTok{(z[z$n_sites >}\DecValTok{0}\NormalTok{, ], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =} \StringTok{`}\DataTypeTok{Markov network}\StringTok{`}\NormalTok{, }\DataTypeTok{y =} \NormalTok{truth)) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_binhex}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{100}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Estimated coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}"}\StringTok{True}\CharTok{\textbackslash{}"}\StringTok{ coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{scale_fill_gradient}\NormalTok{(}\DataTypeTok{low =} \StringTok{"#F0F0F0"}\NormalTok{, }\DataTypeTok{high =} \StringTok{"darkblue"}\NormalTok{, }\DataTypeTok{trans =} \StringTok{"identity"}\NormalTok{) +}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() +}\StringTok{ }
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Markov network"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_abline}\NormalTok{(}\DataTypeTok{intercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{slope =} \KeywordTok{coef}\NormalTok{(}\KeywordTok{lm}\NormalTok{(z$truth ~}\StringTok{ }\NormalTok{z$}\StringTok{`}\DataTypeTok{Markov network}\StringTok{`} \NormalTok{+}\StringTok{ }\DecValTok{0}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\includegraphics{recovery_files/figure-latex/unnamed-chunk-8-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{(z[z$n_sites >}\DecValTok{0}\NormalTok{, ], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =} \StringTok{`}\DataTypeTok{Pairs}\StringTok{`}\NormalTok{, }\DataTypeTok{y =} \NormalTok{truth)) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_binhex}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{100}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Estimated coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}"}\StringTok{True}\CharTok{\textbackslash{}"}\StringTok{ coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{scale_fill_gradient}\NormalTok{(}\DataTypeTok{low =} \StringTok{"#F0F0F0"}\NormalTok{, }\DataTypeTok{high =} \StringTok{"darkblue"}\NormalTok{, }\DataTypeTok{trans =} \StringTok{"identity"}\NormalTok{) +}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() +}\StringTok{ }
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Null model (}\CharTok{\textbackslash{}"}\StringTok{Pairs}\CharTok{\textbackslash{}"}\StringTok{)"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_abline}\NormalTok{(}\DataTypeTok{intercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{slope =} \KeywordTok{coef}\NormalTok{(}\KeywordTok{lm}\NormalTok{(z$truth ~}\StringTok{ }\NormalTok{z$Pairs +}\StringTok{ }\DecValTok{0}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\includegraphics{recovery_files/figure-latex/unnamed-chunk-8-2.pdf}

@@

\begin{verbatim}
## R-squared is 1.23-1.29 times higher than from partial correlation (95% bootstrap CI)
## R-squared is 1.79-1.95 times higher than from correlation (95% bootstrap CI)
## R-squared is 1.14-1.18 times higher than from GLM (95% bootstrap CI)
## R-squared is 2.72-3.28 times higher than from BayesComm (95% bootstrap CI)
## R-squared is 1.29-1.37 times higher than from partial BayesComm (95% bootstrap CI)
## R-squared is 2.12-2.37 times higher than from Pairs (95% bootstrap CI)
\end{verbatim}

>>>>

\CommentTok{# Run all the analyses on all the files}
\NormalTok{z =}\StringTok{ }\KeywordTok{lapply}\NormalTok{(files, fit_all) %>%}\StringTok{ }\NormalTok{bind_rows %>%}\StringTok{ }\NormalTok{as.data.frame}

\CommentTok{# Fix a formatting issue with the column names}
\KeywordTok{colnames}\NormalTok{(z) =}\StringTok{ }\KeywordTok{gsub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{."}\NormalTok{, }\StringTok{" "}\NormalTok{, }\KeywordTok{colnames}\NormalTok{(z))}
\end{Highlighting}
\end{Shaded}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# R-squareds computed across *all* landscape types}
\NormalTok{total_ss =}\StringTok{ }\KeywordTok{mean}\NormalTok{(}\KeywordTok{resid}\NormalTok{(}\KeywordTok{lm}\NormalTok{(truth ~}\StringTok{ }\DecValTok{0}\NormalTok{, }\DataTypeTok{data =} \NormalTok{z))^}\DecValTok{2}\NormalTok{)}
\KeywordTok{round}\NormalTok{(}\DecValTok{100} \NormalTok{*}\StringTok{ }\KeywordTok{sort}\NormalTok{(}\DecValTok{1} \NormalTok{-}\StringTok{ }\KeywordTok{colMeans}\NormalTok{(resids^}\DecValTok{2}\NormalTok{) /}\StringTok{ }\NormalTok{total_ss), }\DecValTok{1}\NormalTok{)}

\CommentTok{# Rank correlations among the methods that estimate marginal relationships}
\KeywordTok{round}\NormalTok{(}\KeywordTok{cor}\NormalTok{(z[ , }\KeywordTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{12}\NormalTok{)], }\DataTypeTok{method =} \StringTok{"spearman"}\NormalTok{)[,}\DecValTok{1}\NormalTok{], }\DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\KeywordTok{ggplot}\NormalTok{(z[z$n_sites >}\DecValTok{0}\NormalTok{, ], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =} \StringTok{`}\DataTypeTok{Markov network}\StringTok{`}\NormalTok{, }\DataTypeTok{y =} \NormalTok{truth)) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_binhex}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{100}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Estimated coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}"}\StringTok{True}\CharTok{\textbackslash{}"}\StringTok{ coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{scale_fill_gradient}\NormalTok{(}\DataTypeTok{low =} \StringTok{"#F0F0F0"}\NormalTok{, }\DataTypeTok{high =} \StringTok{"darkblue"}\NormalTok{, }\DataTypeTok{trans =} \StringTok{"identity"}\NormalTok{) +}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() +}\StringTok{ }
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Markov network"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_abline}\NormalTok{(}\DataTypeTok{intercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{slope =} \KeywordTok{coef}\NormalTok{(}\KeywordTok{lm}\NormalTok{(z$truth ~}\StringTok{ }\NormalTok{z$}\StringTok{`}\DataTypeTok{Markov network}\StringTok{`} \NormalTok{+}\StringTok{ }\DecValTok{0}\NormalTok{)))}

\NormalTok{z$}\StringTok{`}\DataTypeTok{-Pairs}\StringTok{`} \NormalTok{=}\StringTok{ }\NormalTok{-z$Pairs}
\KeywordTok{ggplot}\NormalTok{(z[z$n_sites >}\DecValTok{0}\NormalTok{, ], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =} \StringTok{`}\DataTypeTok{-Pairs}\StringTok{`}\NormalTok{, }\DataTypeTok{y =} \NormalTok{truth)) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_binhex}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{100}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"Estimated coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}"}\StringTok{True}\CharTok{\textbackslash{}"}\StringTok{ coefficient value"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{size =} \DecValTok{1}\NormalTok{/}\DecValTok{8}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{scale_fill_gradient}\NormalTok{(}\DataTypeTok{low =} \StringTok{"#F0F0F0"}\NormalTok{, }\DataTypeTok{high =} \StringTok{"darkblue"}\NormalTok{, }\DataTypeTok{trans =} \StringTok{"identity"}\NormalTok{) +}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() +}\StringTok{ }
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Null model (}\CharTok{\textbackslash{}"}\StringTok{Pairs}\CharTok{\textbackslash{}"}\StringTok{)"}\NormalTok{) +}\StringTok{ }
\StringTok{  }\KeywordTok{stat_abline}\NormalTok{(}\DataTypeTok{intercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{slope =} \KeywordTok{coef}\NormalTok{(}\KeywordTok{lm}\NormalTok{(z$truth ~}\StringTok{ }\NormalTok{z$}\StringTok{`}\DataTypeTok{-Pairs}\StringTok{`} \NormalTok{+}\StringTok{ }\DecValTok{0}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{save}\NormalTok{(results, sizes, }\DataTypeTok{file =} \StringTok{"graph_data.Rdata"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
